% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Xiao Bao Luo}

\basicInfo{
    \email{1944303766@qq.com} \textperiodcentered\
    \phone{18296651587}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Xidian University}, XiAn, ShanXi}{2020 -- Present}
\textit{Master student} in Electronics Engineering (EE), expected June 2023
\datedsubsection{\textbf{East China University of Technology}, NanChang, JiangXi}{2016 -- 2020}
\textit{B.S.} in Information and Computing Sciences

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Audio quality optimization} guangzhou China}{Mar. 2021 -- Present}
\role{Intern}{Lab Project}
This is my lab project, and I am responsible for the VAD(Voice Activity Detection) module. I have completed
\begin{itemize}
    \item extract the VAD module out of webrtc, and compile it on the company platform.
    \item use pytorch to train the deep learning algorithm, it eventually achieved 85\% accuracy on the dataset.
\end{itemize}

\datedsubsection{\textbf{C++ Web Server}}{Jun. 2021 -- Present}
\role{C++}{Individual Project}
A web server with C++11.
\begin{itemize}
    \item The high concurrency model of Reactor of multithreading was realized by thread pool and epoll.
    \item The finite state machine is used to parse HTTP request and process static resource requests.
    \item The GET and POST method in HTTP are resolved.
    \item A timer based on a small root heap implementation that closes inactive connections that have timed out.
\end{itemize}

\datedsubsection{\textbf{Json parser}}{Jun. 2020 -- Dec. 2020}
\role{C}{Individual Project}
Json parser written in C, able to parse standard JSON format and string.
\begin{itemize}
    \item A JSON parser conforming to the ECMA-404 standard is written using a recursive descent parser.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
    \item Programming Languages: C == Python > C++ > Java
    \item Platform: Linux
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{Second-class Scholarship for Graduate Students}{2021}
\datedline{First-class Scholarship for Graduate Students }{2020}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
    \item Blog: https://lxb1226.github.io/
    \item GitHub: https://github.com/lxb1226
    \item Languages: English - CET6
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
